### 2020-10-15 conclusion.tex
Compressed lists and subsubsections, minor rewrites in text.
Compressed PCP metatheory.
Minor changes.

\subsubsection*{Conclusion and Future Work}
In this paper we presented Priority GV, which is a functional language with session types. We used priorities in session types, following Priority CP~\cite{dardhagay18} to guarantee deadlock freedom statically via our priority-based type system. We proved the progress property of PGV in \cref{lem:pgv-closed-progress-confs}. We also presented an updated version of PCP, where we moved from commuting conversions to structural congruence in the reduction relation, thus remaining faithful to the reduction relation of the $\pi$-calculus. Finally, we presented an encoding of Priority CP to Priority GV in \cref{sec:priority-cp}. For this translation we proved that it is sound with respect to typing (\cref{thm:pcp-to-pgv-confs-preservation}) and operational semantics, given by operational correspondence soundness (\cref{thm:pcp-to-pgv-operational-correspondence-soundness}) and completeness (\cref{thm:pcp-to-pgv-operational-correspondence-completeness}).

We identify the following main directions for future work: exploring recursion in PGV, by integrating the works of Lindley and Morris~\cite{lindleymorris16} and Padovani and Novara~\cite{padovaninovara15}; defining a translation from Priority GV to Priority CP; and adding sharing following Balzer and Pfenning~\cite{balzerpfenning17}.
\end{document}

>>>>

\subsubsection*{Conclusion and Future Work}
We presented Priority GV, a~session-typed functional language which uses priorities to ensure deadlock freedom, and showed its relation to Priority CP~\cite{dardhagay18} via an operational correspondence.

Our formalism so far only captures the core of GV. In future work, we plan to explore: recursion in PGV, by integrating the works of Lindley and Morris~\cite{lindleymorris16} and Padovani and Novara~\cite{padovaninovara15}; a~translation from Priority GV to Priority CP; and sharing, following Balzer and Pfenning~\cite{balzerpfenning17}.
\end{document}
